\bf Excuse me, do you have a moment to talk about version control?

### 2017-06-29 README.Rmd
Work on first figure

```{r commit-diff-sha-tag, fig.cap="\\label{fig:commit-diff-sha-tag}Partial commit history for our iris example."}
knitr::include_graphics("commit-diff-sha-tag.png")
```

>>>>

```{r commit-diff-sha-tag, fig.cap="\\label{fig:commit-diff-sha-tag}Partial commit history for our iris example, highlighting diffs, commit messages, SHAs, and tags."}
knitr::include_graphics("commit-diff-sha-tag.png")
```

### 2017-06-29 README.tex
Work on first figure

\begin{figure}
\includegraphics[width=1\linewidth]{commit-diff-sha-tag} \caption{\label{fig:commit-diff-sha-tag}Partial commit history for our iris example.}\label{fig:commit-diff-sha-tag}
\end{figure}

>>>>

\begin{figure}
\includegraphics[width=1\linewidth]{commit-diff-sha-tag} \caption{\label{fig:commit-diff-sha-tag}Partial commit history for our iris example, highlighting diffs, commit messages, SHAs, and tags.}\label{fig:commit-diff-sha-tag}
\end{figure}
